\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-05-14 paper/paper.tex
Format fix
CCS ACM format
pass up to implementation

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix2019_v3}

% For submission make this a noop

@@

@@

%for single author (just remove % characters)
%\author{
%{\rm Your N.\ Here}\\
%Your Institution
%\and
%{\rm Second Name}\\
%Second Institution
%% copy the following lines to add more authors
%% \and
%% {\rm Name}\\
%%Name Institution
%} % end author

@@

@@

For example, domain fronting~\cite{meek} was a popular circumvention
strategy used by Meek (in Tor), as well as by the Signal secure messaging app to
get around censorship in countries where it was
blocked~\cite{signal,signal-domain-fronting}.
But in May~2018, Google and Amazon made both technical and policy changes to
their cloud infrastructures that removed support for domain
fronting~\cite{aws-front}. While meek
continues to use other cloud providers that (for now) continue to allow domain
fronting, Signal abandoned the strategy altogether~\cite{signal-back-on-front}.
There is an urgent need for new, more robust approaches to circumvention.

@@

Phantom hosts are cheap to create, allowing for discardable or even one-time-use
proxy servers. This greatly increases the cost for censors to
block, as they must detect and block in real time. Meanwhile, even a censor that
can detect 90\% of phantom hosts does not significantly increase the cost to the
circumvention system, giving \scheme an advantage in the censor/circumventor
cat-and-mouse game.
\scheme supports both IPv4 and IPv6, though we note that the technique is especially
powerful in IPv6, where censors cannot exhaustively scan the address space
ahead of time to identify addresses that change behavior.
Because we fully control the transport connection, connections can live as
long as needed, without the complexity faced by TapDance.

@@

We introduce the \scheme protocol (Section~\ref{sec:architecture})
and analyze its security, finding that it resists a broader
range of detection attacks than TapDance.
We have implemented a prototype implementation (Section~\ref{sec:implementation})
and deployed it on a 10~Gbps testbed similar to the TapDance
deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
\scheme has reduced complexity and substantially improved performance
(Section~\ref{sec:evaluation}).  We believe that these advantages
make \scheme a strong choice for future Refraction Networking deployments.

@@

Our deployment model is identical to that of TapDance: we only require a passive
tap at the deploying ISP, and the ability to inject (spoofed) traffic from phantom
hosts.
Furthermore, we assume
asymmetric routing (i.e. that the tap can sometimes only see packets from but not to the
client).
However, we assume a stronger threat model for the adversary than
TapDance, as our design resists active attacks.

We assume the censor can block arbitrary IP addresses and networks, but faces a
cost in doing so if it blocks potentially useful resources. In particular, we
assume it is difficult for the censor to have complete knowledge of legitimate
addresses used, and so instead resorts to a blacklist approach to blocking
proxies and objectionable content.
Whitelists are expensive for censors to maintain and can stifle
innovation, and are rarely employed by censors.

We assume that the censor can know what network the \scheme station(s) are
deployed in and the prefixes phantom hosts are selected from, but that blocking those
networks outright brings a collateral
damage the censor is unwilling to suffer. Instead, the censor aims to identify
the addresses that are phantom hosts, and block only those.

We assume the censor can use the client to register and access its own phantom
hosts, but that these will not reveal the phantom hosts of other users. The
censor can also actively probe addresses that it sees users accessing, but can
not enumerate the entire ISP prefix (e.g. a /32 IPv6 prefix contains
$2^{96} addresses$).

Finally, we assume the censor can replay or preplay any connections that it
suspects involve phantom hosts (or their registration) in an attempt to confirm.
However, the censor wishes to avoid disrupting any connections before it
knows for certain they are from \scheme clients, lest they disrupt legitimate
connections. This means that injecting false data or corrupting TLS sessions is
outside the scope of the censor, but that the censor can send non-disruptive
probes (such as stale TCP acknowledgements or other packets that would normally
be ignored). We emphasize that TapDance is observable by censors that can send
TCP packets in suspected connections, but that our protocol is robust against
this class of censor.

@@

\scheme involves three main steps. First, clients \textbf{register} with the
ISP station,
and agree on the phantom host IP address that will be used. Next, the client
connects to the agreed upon address, which is terminated by an
\textbf{application} running on the station. Finally, the client \textbf{proves}
to the application that it was the same client that registered (and not a censor
attempting to probe), and is able to use the application as a proxy.

Similar to previous schemes, our design does not require expensive in-line
flow blocking, and can be accomplished with only a passive tap at the ISP.
Our architecture is also modular, in that the registration and application steps operate
independently, allowing a wide range of flexibility to evade censors. We
describe each of these components.

@@

Clients can register intent to use the proxy in several covert ways. For
instance, they could use email or other existing intermittently available proxies
to register. In this section, we use a form of Refraction Networking similar to
TapDance to register directly with the station.

@@

To register, clients connect to a \textbf{decoy} site that supports TLS. They
complete the handshake, and send a normal HTTPS request that embeds a special
steganographic \textbf{tag} in the ciphertext of the request. We use
the same technique used in TapDance's covert ciphertext channel\footnote{Section 3 in
TapDance~\cite{tapdance14}} to embed the tag, but we purposefully have the client
send a complete request (rather than incomplete), allowing the decoy server to respond.
The steganographic tag is only visible to the ISP station, which can see the tag using its
private key. Unlike in TapDance, the \scheme station can passively observe
the tag, and does not need to respond to it (which requires mimicking the
decoy)

The tag contains a public key (encoded to be indistinguishable from random using
Elligator~\cite{elligator}), and a message encrypted under the shared secret
derived from a key exchange with the station's long-term public key hard-coded
in the client software. The station uses its private key to compute the same
shared secret from the (decoded) public key, and decrypts the message in the
tag. The censor, without knowledge of either the station or client's private
key, cannot derive the shared secret, preventing it from being able to decrypt
the message, or even learn of its existence.

Inside the message, the client communicates a random \textbf{seed}, and other
configuration-specific information, such as flags to signify version, feature
support, and a set of IPv6 network prefixes that the client knows can be used
for phantom hosts (previously distributed publicly).
The client and server hash the seed to determine which specific
IPv6 address from the set of prefixes will be used and registered as a phantom host. It may seem intuitive to instead have the client
send the specific IP address to register, but allowing the client arbitrary
choice also allows the censor to register suspected phantom hosts and block them if
they pick up. 
By using a hash of a seed, the censor would have to pre-image the hash to
obtain a seed it could use to register for a desired IP address.
It also gives a
secret (the seed) that only the client and station know, even after the client
connects to the phantom host address.

Once the phantom host IP address has been selected, the station watches for
packets destined to that address, and forwards them onto the phantom host
\textbf{application}. The station can also optionally ignore packets not from
the source IP address of the registering client, so that to a probing censor
from a different IP address,
the phantom host appears to be firewalled off from all but the client. We note
this is not a robust solution: censors have previously been observed taking over
IP addresses of clients~\cite{ensafi-tor}. We instead address active probing in
the application.

@@

In addition, the use of IPv6 prevents censors from exhaustively probing
potential phantom host network prefixes ahead of time to learn the full set of
legitimate sites in the network.

\paragraph{IPv4}
While \scheme composes well with IPv6, we can also support IPv4,
at the cost of being vulnerable to active probing by the censor.
We emphasize that TapDance is already
vulnerable to active probing attacks~\cite{tapdance14} that \scheme defends
against when using IPv6. However, in IPv4, there are substantially fewer
addresses, allowing censors to easily enumerate network prefixes that pass by
the ISP station and measure legitimate sites. Furthermore, the small address
space makes it much easier to pre-image the hash used to derive IP addresses
from the seed. Registering a specific IPv4 address in an IPv4 /16 subnet will
take only an expected $2^{16}$ hashes for the censor to achieve. This would let
attackers register legitimate hosts as phantom hosts, potentially disrupting
legitimate service. If the station refused to pick up for addresses that
correspond to legitimate hosts (measured by scanning during registration), then
censors could use this as an oracle for distinguishing legitimate sites from
phantom hosts. Still, IPv4 \scheme offers many performance, flexibility, and
simplicity benefits over TapDance, though they are both vulnerable to active
probing attacks.

@@

Once the client has registered, packets sent to the phantom host IP address are
passed to the \textbf{application} running on the station. The application has
two main jobs: first, it must look like an innocuous legitimate service to the
censor, and second must allow the client to use it as a proxy.

Any protocol that satisfies these criteria can be used as an application. For
instance, \texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
Tor~\cite{tor} that could be
modified to meet these needs: it requires each endpoint to have knowledge of a
shared secret (which we can derive from the seed shared by the client and
station during registration), and attempts to be a protocol with no discernible
fingerprint. Probing censors that do not have the shared secret receive no
response, while clients that have the secret can communicate with the proxy.

However, even though \texttt{obfs4} is indistinguishable from random, there are
still known attacks that can differentiate it from other
traffic~\cite{wang2015seeing}. While we have yet to see evidence of such attacks
employed in practice by censors, we consider two alternatives built on TLS.

@@

@@

This is because TLS sends important server-identifying content in plaintext
during the TLS handshake. This includes the Server Name Indication (SNI) in the
Client Hello message that sends the domain name of the server, and the
X.509 Certificate sent by the server.

To evade censors, we must send a plausible SNI value (sending no SNI is
uncommon and easily blocked---study conducted using Colorado University network
infrastructure shows that only 1\% of all TLS connections coming in and out of 
campus do not carry the
SNI extension~\cite{tls-fingerprint}), and we must have the server respond with
a plausible (and corresponding) certificate. Even if we manage to avoid sending
either in the clear, censors could actively probe the server in a
way that would normally elicit a certificate.

We therefore attempt to mimic an existing \textbf{mask site}, by relaying
traffic between the client and a selected mask website. To a censor, this site
will be indistinguishable from the legitimate mask site, making it difficult for
them to block without potentially blocking the actual site. TLS connections to the
application will terminate exactly as connections to the mask site would, with the
application acting as a transparent proxy between the client and mask site.
However, this leaves the application unable to introspect on the contents of the
TLS connection to the mask site, as it does not have the client-site shared
secrets, and it cannot overtly man-in-the-middle the connection before knowing
it is communicating with the legitimate client (and not the censor).

To accomplish this, the client changes the shared secret it derives with the
mask site to something that the application can also derive. The client's first
\texttt{Application Data} packet is thus encrypted under a different secret than
the client/mask site secret. Specifically, the client uses the \textbf{seed}
sent during registration to derive the pre-master secret for the connection.
This is hashed along with the client and server randoms of the current (mask
site) TLS connection to obtain the master secret that determines
encryption/decryption/authentication keys.

@@

However, there are proposals to encrypt the SNI in the Client Hello~\cite{ietf-tls-esni-02},
though none have been implemented or deployed as of early 2019. Nonetheless,
if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
\scheme applications by allowing the domain to remain hidden from the censor.
While the censor could still try to actively probe with guesses for the SNI,
servers could respond with generic ``Unknown SNI'' errors. If such responses
were common for incorrect SNI, the censor's efforts to identify phantom hosts
would be frustrated.

@@

We implemented the \scheme protocol and tested it in a 10~Gbps ISP testbed
with real traffic. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to
consume the 10~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
detector processes all packets and watches for new registrations. It also
forwards all packets sent to a (registered) phantom host address to the local
\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
allowing the application to accept and respond to connections using the native
operating system's interface. Figure~\ref{fig:implementation} shows the overall
architecture of our implementation, which we describe next.
% Along with the client?

>>>>

\documentclass[sigconf]{acmart}
%\usepackage{usenix2019_v3}

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2019}
\acmYear{2019}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[CCS '19]{CCS '19: ACM Conference on Computer and Communications
Security}{November 11--15, 2019}{London, UK}
\acmBooktitle{CCS '19: ACM Symposium on Computer and Communications Security,
  November 11--15, 2019, London, UK}
\acmPrice{0.00}
\acmISBN{978-1-4503-9999-9/18/06}

@@

\widowpenalty=10000
\clubpenalty=10000

@@

%\author{Anonymized for review}
%for single author (just remove % characters)
%\author{
%{\rm Your N.\ Here}\\
%Your Institution
%\and
%{\rm Second Name}\\
%Second Institution
%% copy the following lines to add more authors
%% \and
%% {\rm Name}\\
%%Name Institution
%} % end author

@@

\keywords{anticensorship, proxies, network security}

@@

For example, domain fronting~\cite{meek} was a popular circumvention
strategy used by meek (in Tor), as well as by the Signal secure messaging app to
get around censorship in countries where it was
blocked~\cite{signal,signal-domain-fronting}.
But in May~2018, Google and Amazon made both technical and policy changes to
their cloud infrastructures that removed support for domain
fronting~\cite{aws-front}. While meek
continues to use other cloud providers that (for now) continue to allow domain
fronting, Signal abandoned the strategy altogether~\cite{signal-back-on-front}.
There is an urgent need for new, more robust approaches to circumvention.

@@

Phantom hosts are cheap to create, allowing for discardable or even one-time-use
proxy servers. This greatly increases the cost for censors to
block, as they must detect and block in real time. Meanwhile, even a censor that
can detect 90\% of phantom hosts does not significantly increase the cost to the
circumvention system, giving \scheme an advantage in the censor/circumventor
cat-and-mouse game.
%TODO: don't need to hedge on IPv4 anymore..?
\scheme supports both IPv4 and IPv6, though we note that the technique is especially
powerful in IPv6, where censors cannot exhaustively scan the address space
ahead of time to identify addresses that change behavior.
Because we fully control the transport connection, connections can live as
long as needed, without the complexity faced by TapDance.

@@

% TODO: modularity?

We introduce the \scheme protocol (Section~\ref{sec:architecture})
and analyze its security, finding that it resists a broader
range of detection attacks than TapDance.
We have implemented a prototype implementation (Section~\ref{sec:implementation})
and deployed it on a 10~Gbps testbed similar to the TapDance
deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
\scheme has reduced complexity and substantially improved performance
(Section~\ref{sec:evaluation}).  In addition, \scheme provides significantly
more flexibility than existing Refraction protocols, allowing maintainers to
respond to future censor techniques.
We believe that these advantages
make \scheme a strong choice for future Refraction Networking deployments.

@@

Our deployment model is identical to that of TapDance: we only require a passive
tap at the deploying ISP, and the ability to inject (spoofed) traffic from phantom
hosts.
Furthermore, we assume
asymmetric routing (i.e. that the tap might only see packets from but not to the
client).
However, we assume a stronger threat model for the adversary than
TapDance, as our design resists active attacks.

We assume the censor can block arbitrary IP addresses and networks, but faces a
cost in doing so if it blocks potentially useful resources. In particular, we
assume it is difficult for the censor to have complete knowledge of legitimate
addresses used, and so instead resorts to a blacklist approach to blocking
proxies and objectionable content.
Whitelists are expensive for censors to maintain and can stifle
innovation, and are rarely employed by country-level censors.
%TODO: cite OONI? censored planet?

We assume that the censor can know what network the \scheme station(s) are
deployed in and the prefixes phantom hosts are selected from, but that blocking those
networks outright brings a collateral
damage the censor is unwilling to suffer. Instead, the censor aims to identify
the addresses that are phantom hosts, and block only those. We note this
assumption supposes that the deployment is large enough to deter routing around
decoy attacks~\cite{rad12,true-cost-rad}.

We assume the censor can use the client to register and access its own phantom
hosts, but that these will not reveal the phantom hosts of other users. The
censor can also actively probe addresses that it sees users accessing, and can
employ tools such as ZMap~\cite{zmap13} to scan large network blocks, excepting
large IPv6 prefixes (e.g. a /32 IPv6 prefix contains $2^{96}$ addresses).

Finally, we assume the censor can replay or preplay any connections that it
suspects involve phantom hosts (or their registration) in an attempt to confirm.
However, the censor wishes to avoid disrupting any connections before it
knows for certain they are from \scheme clients, lest they disrupt legitimate
connections. This means that injecting false data or corrupting TLS sessions is
outside the scope of the censor, but that the censor can send non-disruptive
probes (such as stale TCP acknowledgements) that would normally
be ignored. We emphasize that TapDance is observable by censors that can send
TCP packets in suspected connections, but that our protocol is robust against
this class of censor.

@@

\scheme involves two high-level steps. First, clients \textbf{register} with the
ISP station,
and agree on the phantom host IP address that will be used. Then, the client
connects to the agreed upon phantom address, which relays the client's traffic
to an \textbf{application}. If the application determines the traffic is from
the same client that originally registered (and not a probing censor), it
provides access to the proxy, tunneled through the application's protocol.

Similar to previous schemes, our design does not require expensive in-line
flow blocking, and can be accomplished with only a passive tap at the ISP.
Our architecture is also modular, in that the registration and application steps operate
independently, allowing a wide range of flexibility to evade censors. We
describe each of these components, and then describe our implementation and
deployment in Section~\ref{sec:implementation}.

@@

Clients can register intent to use the proxy in several covert ways. For
instance, they could use email~\cite{SWEET-ToN} or any other existing intermittently
available proxies
to register. In this section, we use a form of Refraction Networking similar to
TapDance to register directly with the station, though note our scheme is simpler and more
difficult to detect or block compared to vanilla TapDance.
%We note this form is simpler and more difficult to detect or block than
%TapDance.

@@

To register, clients connect to a \textbf{decoy} site that supports TLS. They
complete the handshake, and send a normal HTTPS request that embeds a special
steganographic \textbf{tag} in the ciphertext of the request. We use
the same technique used in TapDance's covert ciphertext
channel\footnote{Section~3 in
TapDance~\cite{tapdance14}} to embed the tag, but we purposefully have the client
send a complete request (rather than incomplete), allowing the decoy server to respond.
The steganographic tag is only visible to the ISP station, which can see the tag using its
private key. Unlike in TapDance, the \scheme station can passively observe
the tag, and does not need to respond to it (which requires mimicking the
decoy).
%In addition, more potential decoys can be used than in TapDance, as
%there is no need to exclude decoys that have timeouts or TCP windows unfavorable
%for keeping connections open. We estimate in our deployment an increase of 25\%
%in decoys that could be used.

The tag contains a public key (encoded to be indistinguishable from random using
Elligator~\cite{elligator}), and a message encrypted under the shared secret
derived from a Diffie-Hellman key exchange with the station's long-term public key hard-coded
in the client software. The station uses its private key to compute the same
shared secret from the (decoded) client public key, and decrypts the message in the
tag. The censor, without knowledge of either the station or client's private
key, cannot derive the shared secret, preventing it from being able to decrypt
the message, or even learn of its existence.

Inside the message, the client communicates a random \textbf{seed}, and other
configuration-specific information, such as flags to signify version, feature
support, and a set of network prefixes that the client knows can be used
for phantom hosts (previously distributed publicly).
The client and server hash the seed to determine which specific
IP address from the set of prefixes will be used and registered as a phantom host.
It may seem intuitive to instead have the client
send the specific IP address to register, but allowing the client arbitrary
choice also allows the censor to register suspected phantom hosts and block them if
they pick up.
By using a hash of a seed, the censor would have to pre-image the hash to
obtain a seed it could use to register for a desired IP address.
It also gives a
secret (the seed) that only the client and station know, which can
later be used to verify a client connecting to the phantom host address is the
original registering client.

Once the phantom host IP address has been selected, the station watches for
packets destined to that address, and forwards them onto the phantom host
\textbf{application}. The station ignores packets that are not from
the source IP address of the registering client, so that to a probing censor
from a different IP address,
the phantom host appears to be firewalled off from all but the client. We note
that this does not address censors that send follow-up probes, as censors could
take over the IP address of suspected clients for these
probes~\cite{ensafi-tor}. However, it does prevent censors from enumerating the
address space before hand, as they would have to do so from every potential
client IP address. Simply scanning the prefixes with ZMap~\cite{zmap13} from a
single vantage point would not reveal hosts that only respond to specific IPs
(e.g. are firewalled off).
%We instead address active probing in the application.

@@

%In addition, the use of IPv6 prevents censors from exhaustively probing
%potential phantom host network prefixes ahead of time to learn the full set of
%legitimate sites in the network, even from a single vantage point.
%Therefore, IPv6 phantom hosts could choose
%to respond to any client, and not just the original registering client.

\paragraph{IPv4}
While \scheme composes well with IPv6, we can also support IPv4, with some
careful caveats. First, in IPv4, there are substaintially fewer addresses,
allowing censors to easily \textbf{enumerate network prefxies} that pass by the ISP
station to look for legitimate sites to whitelist. However, as previously noted,
having phantom hosts pretend to be firewalled off from all but the registered
client forces censors to have to enumerate from all potential client vantage
points to measure the state of hosts before registration. This whitelist
approach for a censor would also overblock new services that came online after
their scan.
Additionally, for IPv4 \scheme, we dynamically generate the TCP port of the phantom host
during registration (along with its IP), which further makes exhaustive scans infeasible:
a censor that must enumerate from the vantage point of a /10 of client IPs (4~million IPs)
to a /16 (65K IPs) of potential phantom proxies on each of 65K potential ports would take nearly
50~years of scanning with ZMap at 10~Gbps.

A second problem in IPv4 \scheme is that the limited range of IPs (and ports)
makes it possible for a censor to \textbf{pre-image the hash} used to derive the phantom
address from the seed. Even with the /16 of IPs and all 65K ports, a censor need
only test an expecated $2^{32}$ possible seeds to find one that would allow it
to register for that phantom address. The censor could then register a suspected
address, and see if it provides proxy access. If it does, the censor learns
there is no legitimate service there, and can block it. To combat this, we
allow only a single client to register for a particular phantom address at a
time. A censor could attempt to register all addresses in an attempt to deny
proxy service to legitimate users, but this would be easily observed at the
registration system, where rate limits via client puzzles or account-based fees
could be enforced.

Finally, legitimate \textbf{IPv4 addresses density} is much higher than IPv6,
increasing the potential for users to accidentally register seeds that derive
phantom addresses corresponding to live hosts. To address this, the station
sends probes to potential phantom hosts during registration, and ignores the
registration if a real host responds.

%We emphasize that TapDance is already
%vulnerable to active probing attacks~\cite{tapdance14} that \scheme defends
%against when using IPv6. However, in IPv4, there are substantially fewer
%addresses, allowing censors to easily enumerate network prefixes that pass by
%the ISP station and measure legitimate sites. Furthermore, the small address
%space makes it much easier to pre-image the hash used to derive IP addresses
%from the seed. Registering a specific IPv4 address in an IPv4 /16 subnet will
%take only an expected $2^{16}$ hashes for the censor to achieve. This would let
%attackers register legitimate hosts as phantom hosts, potentially disrupting
%legitimate service. If the station refused to pick up for addresses that
%correspond to legitimate hosts (measured by scanning during registration), then
%censors could use this as an oracle for distinguishing legitimate sites from
%phantom hosts. Still, IPv4 \scheme offers many performance, flexibility, and
%simplicity benefits over TapDance, though they are both vulnerable to active
%probing attacks.

@@

Once the client has registered, packets sent to the phantom host IP address are
passed to the \textbf{application} running on the station. The application has
two main requirements: first, the protocol it uses to communicate with the
client must be difficult for the censor to passively detect and block by traffic
inspection. Second, the application must resist active probes by the censor (who
does not know the registration seed).

Any protocol that satisfies these criteria can be used as an application. For
instance, \texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
Tor~\cite{tor} that is designed to address both of these requirements:
it requires each endpoint to have knowledge of a
shared secret (which we can derive from the registration seed),
and attempts to be a protocol with no discernible
fingerprint. Probing censors that do not have the shared secret receive no
response, while clients that have the secret can communicate with the proxy.

%However, even though \texttt{obfs4} is indistinguishable from random, there are
%still known attacks that can differentiate it from other
%traffic~\cite{wang2015seeing}. While we have yet to see evidence of such attacks
%employed in practice by censors, we consider two alternatives built on TLS.

Besides obfs4, we next describe in detail several alternative application
protocols based on SSH, TLS, and WebRTC. These
alternatives neatly demonstrate the flexibility of \scheme in allowing deployments
to support multiple application protocols. Should censors develop ways to
identify and block one protocol, others can still be used to provide proxy
access.

@@

\subsubsection{Obfuscated SSH}

Obfuscated SSH~\cite{ossh} is a protocol that attempts to mask the Secure Shell
(SSH) protocol in a thin
layer of encryption. This makes it difficult for censors to identify using a
regular expression, as there are no identifying headers or fields for a censor
to search for. Instead, Obfuscated SSH clients first send a 16-byte seed, which
is then used to derive a symmetric key that encrypts the rest of the
communication. While this can be passively observable by censors (who can also
derive the key and deobfuscate the protocol), the key derivation is deliberately
slowed by an iterated hash to make such identifcation
expensive (though not impossible) at high speeds.

Obfuscated SSH also does not protect against active probing, as the censor can
easily create their own connections and confirm the server is using the
protocol. Nonetheless, this protocol is used successfully in deployed censorship
circumvention systems~\cite{psiphon}. Obfuscated SSH could also be used as a \scheme
application protocol, though we note it provides no active probing or passive
identifcation resistance.

@@

One challenge is that TLS sends important server-identifying content in plaintext
during the TLS handshake. This includes the Server Name Indication (SNI) in the
Client Hello message that sends the domain name of the server, and the
X.509 Certificate sent by the server.

To evade censors, we must send a plausible SNI value (sending no SNI is
uncommon and easily blocked---only 1\% of TLS connections
do not send the SNI extension~\cite{tls-fingerprint}), and we must have the server respond with
a plausible (and corresponding) certificate. Even if we manage to avoid sending
either in the clear (e.g. using session resumption), censors could actively probe
the server in a way that would normally elicit a certificate.

We therefore attempt to mimic an existing \textbf{mask site} by relaying
traffic between the client and a selected mask website. To a censor, this site
will be indistinguishable from the legitimate mask site, making it difficult for
them to block without potentially blocking the actual site. TLS connections to the
application will terminate exactly as connections to the mask site would, with the
application acting as a transparent proxy between the client and mask site.
However, this leaves the application unable to introspect on the contents of the
TLS connection to the mask site, as it does not have the client-site shared
secrets, and it cannot overtly man-in-the-middle the connection before knowing
it is communicating with the legitimate client (and not the censor).

To covertly signal to the relaying application, the client changes the shared secret
it derives with the
mask site to something that the application can also derive. The client's first
\texttt{Application Data} packet is thus encrypted under a different secret than
the client/mask site secret. Specifically, the client uses the \textbf{seed}
sent during registration to derive the pre-master secret for the connection.
This is hashed along with the client and server randoms of the current (mask
site) TLS connection to obtain the master secret that determines
encryption/decryption/authentication keys.

@@

However, there are proposals to encrypt the SNI in the Client Hello~\cite{ietf-tls-esni-02},
though none have been implemented or deployed as of 2019. Nonetheless,
if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
\scheme applications by allowing the domain to remain hidden from the censor.
While the censor could still try to actively probe with guesses for the SNI,
servers could respond with generic ``Unknown SNI'' errors. If such responses
were common for incorrect SNI, the censor's efforts to identify phantom hosts
would be frustrated.

@@

We implemented the \scheme protocol and deployed it at a 10~Gbps ISP
with real traffic. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to
consume the 10~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
detector processes all packets and watches for new registrations. It also
forwards all packets sent to a (registered) phantom host address to the local
\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
allowing the application to accept and respond to connections using the native
operating system's interface. Figure~\ref{fig:implementation} shows the overall
architecture of our implementation, which we describe next.
% Along with the client?
